---
title: "p8105_hw1_yz4990"
author: "Yucheng Zhao"
date: "2024-09-21"
output: html_document
---


## Problem 1
```{r}
library("palmerpenguins")
library("tidyverse")
```


Load the dataset "penguins," rename it to "penguins_df," and clean the column names.
```{r}
data("penguins", package = "palmerpenguins")
penguins_df = penguins |> 
  janitor::clean_names()
```


Check the first six rows of the dataset
```{r}
head(penguins_df)
```


Get the variable names and size of the dataset.
```{r}
var_names = names(penguins_df)
col_number = ncol(penguins_df)
row_number = nrow(penguins_df)
```


Delete rows with NA values and summary the data.
```{r}
penguins_df = drop_na(penguins_df)
summary(penguins_df)
```


Calculate the mean of flipper length.
```{r}
fl_mean = mean(penguins_df[["flipper_length_mm"]])
```


Make and save the scatter plot.
```{r}
ggplot(penguins_df, aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = factor(species))) + 
  labs(x = "Bill Length in mm", y = "Filpper Length in mm", color = "Species")

ggsave("scatter_plot.pdf", height = 4, width = 6)
```
```



```{r}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
