---
title: "p8105_hw1_yz4990"
author: "Yucheng Zhao"
date: "2024-09-21"
output: html_document
---


## Problem 1
```{r}
library("palmerpenguins")
library("tidyverse")
```


**Load the dataset "penguins," rename it to "penguins_df," and clean the column names.**
```{r}
data("penguins", package = "palmerpenguins")
penguins_df = penguins |> 
  janitor::clean_names()
```


**Summarize the data and get the variable names and size of the dataset**
```{r}
var_names = names(penguins_df)
col_number = ncol(penguins_df)
row_number = nrow(penguins_df)

summary(penguins_df)
```


**Delete rows with NA values, get mean flipper length**
```{r}
penguins_df = drop_na(penguins_df)

unique_species = unique(penguins_df[["species"]])
unique_island = unique(penguins_df[["island"]])
unique_sex = unique(penguins_df[["sex"]])
unique_year = unique(penguins_df[["year"]])

fl_mean = mean(penguins_df[["flipper_length_mm"]])
```
Here is a short description of the penguins dataset and its variables:

1. species: The species of penguins in the dataset. There are `r length(unique_species)` unique species, which are `r unique_species`. 
1. island: Islands that the penguins are from. There are `r length(unique_island)` unique islands, which are `r unique_island`. 
1. bill_length_mm: Bill length of penguins in mm. The range of this variable is [`r range(penguins_df[["bill_length_mm"]])`].
1. flipper_length_mm: Flipper length of penguins in mm. The range of this variable is [`r range(penguins_df[["flipper_length_mm"]])`].
1. body_mass_g: Body mass of the penguins in g. The range of this variable is [`r range(penguins_df[["body_mass_g"]])`].
1. sex: Sex of the penguins. There are `r length(unique_sex)` sex among the penguins, being `r unique_sex`.
1. year: Years when the data is collected. The data are collected in `r length(unique_year)` years, including `r unique_year`.

The dataset has `r col_number` variables, which are: `r var_names`. The size of the data consists of `r col_number` columns and `r row_number` rows. The rows with 'NA' values are removed latter. 

The mean flipper length of the penguins is `r fl_mean`mm.

**Check the first six rows of the dataset.**
```{r}
head(penguins_df)
```



**Make and save the scatter plot.**
```{r}
ggplot(penguins_df, aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = factor(species))) + 
  labs(x = "Bill Length in mm", y = "Filpper Length in mm", color = "Species")

ggsave("scatter_plot.pdf", height = 4, width = 6)
```



## Problem 2

**Create the data frame**
```{r}
p2_df = tibble(
  vec_rand = rnorm(10),
  vec_logi = vec_rand > 0,
  vec_char = c("a", "b", "c", "abc", "d", "e", "f", "def", "g", "h"),
  vec_fact = factor(c("bad", "bad", "bad", "average", "average", "average", "good", "good", "good", "good"))
)
mean(pull(p2_df, vec_rand))
mean(pull(p2_df, vec_logi))
mean(pull(p2_df, vec_char))
mean(pull(p2_df, vec_fact))
```
**Change the non-numeric vectors to numeric, not showing the result**
```{r, eval = FALSE}
as.numeric(pull(p2_df, vec_logi))
as.numeric(pull(p2_df, vec_char))
as.numeric(pull(p2_df, vec_fact))
```
- The logic vector becomes `r as.numeric(pull(p2_df, vec_logi))` after changing to numeric because r converts 'FALSE' to 0 and 'TRUE' to 1. This explains why the mean of the logic vecotor is `r mean(pull(p2_df, vec_logi))`.
- The character vector becomes `r as.numeric(pull(p2_df, vec_char))` after changing to numeric because as.numeric() will return NA's for characters as they do not have a numeric meaning. This explains why the mean of the character vector is `r mean(pull(p2_df, vec_char))`.
- The factor vector also becomes `r as.numeric(pull(p2_df, vec_fact))` after changing to numeric because the level of the factors are converted to 1, 2, and 3 as there are 3 factors. When trying to take the mean, r returns `r mean(pull(p2_df, vec_fact))` because the mean() function can not be implied to factor vectors directly before converting to numeric. 


