---
title: "p8105_hw1_yz4990"
author: "Yucheng Zhao"
date: "2024-09-21"
output: html_document
---


## Problem 1
```{r}
library("palmerpenguins")
library("tidyverse")
```


Load the dataset "penguins," rename it to "penguins_df," and clean the column names.
```{r}
data("penguins", package = "palmerpenguins")
penguins_df = penguins |> 
  janitor::clean_names()
```


Summarize the data and get the variable names and size of the dataset.
```{r}
var_names = names(penguins_df)
col_number = ncol(penguins_df)
row_number = nrow(penguins_df)

summary(penguins_df)
```
Here is a summary of the dataset penguins. The dataset has `r col_number` variables, which are: `r var_names`. The size of the data consists of `r col_number` columns and `r row_number` rows. The rows with 'NA' values are removed latter. 


Check the first six rows of the dataset.
```{r}
head(penguins_df)
```


Delete rows with NA values and calculate the mean of flipper length.
```{r}
penguins_df = drop_na(penguins_df)
fl_mean = mean(penguins_df[["flipper_length_mm"]])
```
The mean flipper length in mm of the penguins is `r fl_mean`. 

Make and save the scatter plot.
```{r}
ggplot(penguins_df, aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = factor(species))) + 
  labs(x = "Bill Length in mm", y = "Filpper Length in mm", color = "Species")

ggsave("scatter_plot.pdf", height = 4, width = 6)
```
```



```{r}

```

